Papers

### 2023-03-17 papers.qmd
fix doi

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics *, /10.1016/j.cam.2023.115126, 2022. [PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)

>>>>

J. Upston, D. Sulsky, **J. D. Tucker**, and Y. Guan, "CIEL\*Ch color map for visualization and analysis of sea ice motion", *Journal of Computational and Applied Mathematics*, 10.1016/j.cam.2023.115126, 2022. [PDF](Papers/1-s2.0-S0377042723000705-main.pdfupda)
